
---
title: "Suits Viewership Report"
format: html
execute:
  echo: false
---

#Description

Suits is an American legal drama television series created by Aaron Korsh. The show premiered on USA Network on June 23, 2011, and follows talented college dropout Mike Ross, who begins working as a law associate for Harvey Specter despite never having attended law school. The series combines legal drama with character-driven storytelling, focusing on corporate law cases and interpersonal dynamics within the firm.

2. Show Image

3. Basic Statistics
Total seasons: 9
Total episodes: 134
Premiere viewership: ~4.64 million viewers
Peak viewership: ~4.64 million viewers (Season 1 premiere)
Final episode viewership: ~1.04 million viewers
Average viewership trend: Declining over time with some fluctuations
4. Viewership Over Time


```{r}

library(ggplot2)

# Approximate season-average viewership (millions)
seasons <- 1:9
viewers <- c(4.2, 3.5, 3.0, 2.5, 2.2, 1.8, 1.5, 1.3, 1.1)

df <- data.frame(seasons, viewers)

ggplot(df, aes(x = seasons, y = viewers)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Average Viewership of Suits by Season",
    x = "Season",
    y = "Viewers (millions)"
  )
```

```{r}
  changes <- diff(viewers)
df_changes <- data.frame(
  seasons = seasons[-1],
  changes = changes
)

ggplot(df_changes, aes(x = seasons, y = changes)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Season-to-Season Change in Viewership",
    x = "Season",
    y = "Change in Viewers (millions)"
  )
```



  6. Observed Trends

The viewership of Suits shows a clear downward trend over its nine-season run.

From Season 1 (~4.2M) to Season 3 (~3.0M), the show lost approximately 1.2 million viewers.
Between Season 3 and Season 5, viewership declined further by about 0.8 million.
The most gradual decline occurred between Seasons 6 and 9, where the audience dropped from ~1.8M to ~1.1M, a decrease of roughly 0.7 million.

Overall, the series lost around 3.1 million viewers from its early peak to its final season. Despite the decline, the show maintained a consistent audience and strong cultural impact, especially due to streaming popularity after its original broadcast.

7. Notes
Data is based on reported Nielsen ratings summarized on Wikipedia.
Values are season averages (approximated for clarity in visualization).